Characteristic polynomials of p-adic matrices

### 2017-02-03 charpoly/charpoly.tex
Plan of the introduction

@@

\subsection{Notation} Throughout the paper, $K$ will refer to a complete,
discrete valuation field, $\val : K \twoheadrightarrow \Z \cup \{+\infty\}$ to its valuation,
$\OK$ its ring of integers and $\pi$ a uniformizer.

@@

>>>>

\todo{Explain here why computing characteric polynomial is so important}

\todo{Explain also why taking care of precision is important}

@@

\noindent
{\bf Previous contributions.}
\todo{Many \emph{ad-hoc} for Kedlaya-like counting point algorithms.
Our previous paper. What else?}

\noindent
{\bf The contribution of this paper.}

\noindent
{\bf Organization of the article.}

\noindent
{\bf Notations.}
Throughout the paper, $K$ will refer to a complete, discrete valuation 
field, $\val : K \twoheadrightarrow \Z \cup \{+\infty\}$ to its 
valuation, $\OK$ its ring of integers and $\pi$ a uniformizer.

@@

\begin{rem}
The keyword \texttt{algorithm="df"} forces \texttt{SageMath} to use the 
division free algorithm of \cite{}. It is likely that, proceeding so, we 
limit the loss of precision.
\end{rem}
